%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Documentation for the tikzmarmots package
% A package to bring little marmots into tikz
% Maintained by samcarter
%
% Project repository and bug tracker:
% https://github.com/samcarter/tikzmarmots
%
% Released under the LaTeX Project Public License v1.3c or later
% See http://www.latex-project.org/lppl.txt
%
% Version 1.0
% Nov 8, 2018
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% !TeX program = txs:///arara
% arara: latexmk: {
% arara: --> engine: pdflatex,
% arara: --> options: [
% arara: -->    '-shell-escape',
% arara: -->    '-synctex=1',
% arara: -->    '-interaction=nonstopmode',
% arara: -->  ]
% arara: --> }
\documentclass[parskip=half]{scrartcl}

% meta %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The \texorpdfstring{\tikzmarmots}{tikzmarmots} package}
\subtitle{using marmots in \TikZ}
\author{%
  \texorpdfstring{
    \begin{tikzpicture}
     \marmot
    \end{tikzpicture}\\[0.8em]
    \texttt{samcarter}\\
    \url{https://github.com/samcarter/tikzmarmots}\\
    \url{https://www.ctan.org/pkg/tikzmarmots}
  }{samcarter}}
\date{Version 1.0 -- \today}

\usepackage[
  themecolor=sammagenta
]{\jobname-settings}

\colorlet{blue}{samlblue}

\usepackage{tikzducks}
\usetikzlibrary{ducks}
\usepackage{tikzmarmots}
\usetikzlibrary{marmots}
\usepackage{marvosym}
\usepackage{fontawesome}

% customisation %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\footnotemargin}{0.7em}
\setlength{\footheight}{45pt}

\cfoot{%
  \begin{tikzpicture}[scale=0.5] 
    \marmot
    \duck[invisible,signpost=\scalebox{0.6}{\thepage}]
  \end{tikzpicture}
}
\pagestyle{scrheadings}

\begin{document}
\maketitle
\thispagestyle{scrheadings}

\begin{tcolorbox}[coltext=themecolor,width=.8\textwidth,center,sidebyside=false,bottom=10pt,top=10pt]
The \tikzmarmots package was merged into the Ti\emph{k}Zlings package. To get an up-to-date version, please load the \saminline|tikzlings-marmots| or the more general \saminline|tikzlings| package instead.
\end{tcolorbox}


\section{Introduction}
\label{intro}

Inspired by the enthusiasms of the TeX.Stackexchange user \href{https://tex.stackexchange.com/users/121799/marmot}{@marmot} for beings of the same species, this little package can draw marmots using \TikZ.

Unlike its older sibling, the \tikzducks package, this packages focuses on drawing the marmot itself. Additional accessories are not part of the package, but can be taken from other sources.

This package is work in progress, therefore I would be happy to hear your feedback and ideas how to improve the package. The head version of the source code can be found on \url{github.com/samcarter/tikzmarmots}, including a bug tracker -- please make constructive use of it! 
A more stable package version can be found on \CTAN (\url{www.ctan.org/pkg/tikzmarmots}) and is included in both \miktex and \texlive as \tikzmarmots. 
If you seek any other assistance (not bug reports/feature requests), I suggest asking on \href{https://tex.stackexchange.com}{TeX.Stackexchange}.

Copyright \raisebox{0.2em}{\tiny\fontfamily{cmr}\selectfont\textcopyright}
\texttt{samcarter}. Permission is granted to copy, distribute and\slash or modify this software under the terms of the LaTeX project public licence, version 1.3c or later \url{http://www.latex-project.org/lppl.txt}.

The shown example marmots are purely fictional characters, any resemblance to real marmots or persons is purely coincidental and no copyright infringement is intended.

\section{Usage}

The basic usage is fairly simple, to draw a marmot:
\begin{tcblisting}{title={Basic marmot}}
\begin{tikzpicture}
  \marmot
\end{tikzpicture}
\end{tcblisting}

To customise this basic marmot, the package uses \saminline|pgf| keys. 

These keys can for example be used to change the marmot's colour via \saminline|body=<colour name>|. 

\begin{tcblisting}{title={Blue marmot}}
\begin{tikzpicture}
  \marmot[body=blue]
\end{tikzpicture}
\end{tcblisting}

The colour of the belly and muzzle will use a lighter shade of the selected colour, while a darker shade is chosen for paws, nose and eyes.

The key \saminline|3D| will make the marmot 3-dimensional:

\begin{tcblisting}{title={3D marmot}}
\begin{tikzpicture}
  \marmot[3D]
\end{tikzpicture}
\end{tcblisting}

Keys can also be used to add whiskers to the marmot:

\begin{tcblisting}{title={Whiskers}}
\begin{tikzpicture}
  \marmot[whiskers]
\end{tikzpicture}
\begin{tikzpicture}
  \marmot[whiskers=blue]
\end{tikzpicture}
\end{tcblisting}

Or to make it blush:

\begin{tcblisting}{title={Blushing marmot}}
\begin{tikzpicture}
  \marmot[blush]
\end{tikzpicture}
\end{tcblisting}

Some marmots even show their chisel teeth:

\begin{tcblisting}{title={Chisel teeth}}
\begin{tikzpicture}
  \marmot[teeth]
\end{tikzpicture}
\end{tcblisting}

The marmots also can cast a shadow:

\begin{tcblisting}{title={Shadow}}
\begin{tikzpicture}
  \marmot[shadow]
\end{tikzpicture}
\end{tcblisting}

This ability is important if you want to ask Punxsutawney Phil\footnote{\url{https://en.wikipedia.org/wiki/Punxsutawney_Phil}} on Groundhog Day how the weather is going to be. With a probability derived from the statistics of 120 Groundhog Days\footnote{\url{https://www.livescience.com/32974-punxsutawney-phil-weather-prediction-accuracy.html}} the option \saminline|askphil| might or might not result in a shadow.

\begin{tcblisting}{title={Ask Phil}}
\begin{tikzpicture}
  \marmot[askphil]
\end{tikzpicture}
\end{tcblisting}

If the size of the marmots should be changed or shifted:

\begin{tcblisting}{title={Scaled and shifted marmots}, righthand width=3cm}
\begin{tikzpicture}[scale=0.6]
  \marmot
  \marmot[xshift=90pt, scale=.5,
          yshift=150pt,body=brown!80!gray]
  \marmot[xshift=60pt, scale=.5,
          yshift=100pt,body=brown!80!yellow]
  \marmot[xshift=80pt, scale=.5,
          yshift=50pt,body=brown!80!red]
\end{tikzpicture}
\end{tcblisting}

To make the usage easier for the \TikZ-savvy users, the marmots can also be used as \TikZ library. It can be loaded with \saminline|\usetikzlibrary{marmots}|. In addition to the normal functionality of the \tikzmarmots package, the marmots are now also available as \saminline|pic|. A short example:

\begin{tcolorbox}[title={\TikZ library ``marmots''}]
\begin{samcode}
\documentclass{standalone}

\usepackage{tikz}
\usetikzlibrary{marmots}

\begin{document}

\begin{tikzpicture}
\draw (0,0) pic[
    marmot/body=blue,
    marmot/blush,
  ] {marmot};
\draw (2,0) pic[
    scale=1.4,
  ] {marmot};
\end{tikzpicture}

\end{document}
\end{samcode}

\tcblower
\begin{tikzpicture}
\draw (0,0) pic[
    marmot/body=blue,
    marmot/blush,
  ] {marmot};
\draw (2,0) pic[
    scale=1.4,
  ] {marmot};
\end{tikzpicture}
\end{tcolorbox}

\section{Further customisation}

The above list of available customisations does not sound very exhaustive, but there are basically infinite possibilities for further customisation, as the marmots are just shapes in a \TikZ picture -- all the heavy weapons of the \TikZ package are thus available for further customisation.

\begin{tcblisting}{title={Adding things to the marmot}}
\begin{tikzpicture}
  \marmot
  \fill[blue] (2,0) rectangle (1,1);
\end{tikzpicture}
\end{tcblisting}

%\begin{tcblisting}{title={Monochrome marmot}}
%\begin{tikzpicture}
%  \selectcolormodel{gray}
%  \marmot
%\end{tikzpicture}
%\end{tcblisting}

\section{Re-using accessories from the \tikzducks package}

As already said in the introduction, this package focuses on the marmots themselves and does not provide additional accessories. 
However there is no need to despair! Many of the accessories from the \tikzducks package (\url{https://www.ctan.org/pkg/tikzducks}) can be re-used using the \saminline|invisible| key which will only produce the desired item without a duck.

The marmots are designed to have the same height as the ducks, so many items can be adopted without any modifications. One example:

\addtocounter{footnote}{1}
\begin{tcblisting}{title={Marmot Queen$^{\thefootnote}$}}
%\usepackage{tikzducks}
\begin{tikzpicture}
  \marmot
  \duck[invisible,crown]
\end{tikzpicture}
\end{tcblisting}
\footnotetext[\thefootnote]{The Marmot Queen is inspired by \href{http://www.ilregnodeifanes.it/inglese/summary.htm}{The Fanes' saga}}

Unfortunately not all accessories will work. Some are entirely unsuitable (e.g. clothing which shape was specially designed for the ducks), others can be modified to fit:

\begin{tcblisting}{title={Happy Birthday!}}
%\usepackage{tikzducks}
\begin{tikzpicture}
  \marmot
  \duck[invisible, cake=red!50!violet,
        scale=0.7, xshift=9, yshift=18]
\end{tikzpicture}
\end{tcblisting}

For a complete list of available accessories, please see the documentation of the \tikzducks package 
(\url{https://mirrors.ctan.org/graphics/pgf/contrib/tikzducks/tikzducks-doc.pdf}).

\end{document}